\documentclass[a4paper,10pt]{article}

\usepackage{xunicode,xltxtra,url,parskip} 	%other packages for formatting

\usepackage[usenames,dvipsnames]{xcolor}
%\usepackage[big]{layaureo} 				%better formatting of the A4 page
% an alternative to Layaureo can be ** \usepackage{fullpage} **

\usepackage{titlesec}					%custom \section
\usepackage{footnote}
\usepackage{longtable}
\usepackage[margin=.75in,top=1in,bottom=.5in]{geometry}
\usepackage{enumitem}
\usepackage{tabularx}
\usepackage{colortbl}

\setlist{nosep} % remove space before \itemize

%Setup hyperref package, and colours for links
\usepackage{hyperref}
\definecolor{linkcolour}{rgb}{0,0.2,0.6}
\hypersetup{colorlinks,breaklinks,urlcolor=linkcolour, linkcolor=linkcolour}

%FONTS
\defaultfontfeatures{Mapping=tex-text}
%\setmainfont[SmallCapsFont = Fontin SmallCaps]{Fontin}
%%% modified for Karol Kozioł for ShareLaTeX use
\setmainfont[
SmallCapsFont = Fontin-SmallCaps.otf,
BoldFont = Fontin-Bold.otf,
ItalicFont = Fontin-Italic.otf
]
{Fontin.otf}
%%%

%CV Sections inspired by: 
%http://stefano.italians.nl/archives/26
\titleformat{\section}{\Large\scshape\raggedright}{}{0em}{}[\titlerule]
\titlespacing{\section}{0pt}{5pt}{3pt}

%Tweak a bit the top margin
\addtolength{\voffset}{-1.cm}
\setlength{\parindent}{0pt}

\newcommand{\updateinfo}[1][\today]{\par\vfill\hfill{\scriptsize\color{gray}Last updated: #1}}

%--------------------BEGIN DOCUMENT----------------------
\begin{document}

\pagestyle{empty} % non-numbered pages

\font\fb=''[cmr10]'' %for use with \LaTeX command

%--------------------TITLE-------------
\par{\centering
		{\Large Youngmin \textsc{Park}
	}\par}

%--------------------SECTIONS-----------------------------------
%Section: Personal Data

%Department of Mathematics
%Little Hall 358

\begin{center}
\begin{tabularx}{.8\textwidth}{Xl}

Department of Mathematics & Tel: (412) 805-0283 \\
Little Hall 358 & Email: \href{mailto:park.y@ufl.edu}{park.y@ufl.edu}\\
1400 Stadium Rd. Gainesville, FL 32611  & Web: \href{https://youngmp.github.io}{youngmp.github.io}\\
\end{tabularx}
\end{center}


%Section: Education
\section{Employment}
\begin{tabular}{p{0.2\linewidth}p{0.7\linewidth}}
 \textsc{Aug. 2022}  -- \textsc{Present}  & Assistant Professor \textbf{University of Florida}\vspace{8pt}\\
 \textsc{Sep. 2021}  -- \textsc{Sep. 2022}  & PIMS Postdoctoral Fellow \textbf{University of Manitoba}\newline
 \small Advisor: Stephanie Portet\vspace{8pt}\\
 \textsc{Jun. 2019}  -- \textsc{Jul. 2021}  & Postdoctoral Fellow \textbf{Brandeis University}\newline
 \small Advisor: Thomas Fai\vspace{8pt}\\
 \textsc{May 2018}  -- \textsc{May 2019}   & Postdoctoral Fellow \textbf{University of Pennsylvania}\newline
\small Advisor: Maria N. Geffen\\
\end{tabular}



%Section: Education
\section{Education}
\begin{tabular}{p{0.2\linewidth}p{0.7\linewidth}}
\textsc{Aug.} 2013 -- \textsc{Apr.} 2018 & PhD Mathematics, \textbf{University of Pittsburgh}\newline
Thesis: Dimension Reduction of Neural Models Across Multiple Spatio-temporal Scales | \small Advisor: G. Bard Ermentrout\vspace{8pt}\\
\textsc{Aug.} 2012 -- \textsc{Aug.} 2013 & MS Applied Math \textbf{Case Western}, Cleveland, OH \newline
Thesis:  Infinitesimal Phase Response Curves for Piecewise Smooth Dynamical Systems | \small Advisor: Peter J. Thomas\vspace{8pt}\\
\textsc{Aug.} 2008 -- \textsc{Aug.} 2013& BS Applied Math \textbf{Case Western}, Cleveland, OH\\
&\\
\textit{Additional Training}\\
\textsc{Sep.} 2016 & Max Planck Institute G{\"o}ttingen Advanced Computational Neuroscience \\
\textsc{Aug.} 2015 & Woods Hole MBL Methods in Computational Neuroscience\\
\textsc{Jun.} 2010 & Mathematical Biosciences Institute OSU Summer Program
\end{tabular}

\section{Peer-Reviewed Publications}
\noindent
\renewcommand\labelitemi{\tiny$\bullet$}
\begin{enumerate}[leftmargin=.225in,rightmargin=.1in,itemsep=2pt]
    \item \textbf{Park, Y.}, Fai, T.G.,  ``Coarse-grained Stochastic Model of Myosin-Driven Vesicles into Dendritic Spines.'' Accepted for publication at SIAM Journal on Applied Mathematics (2021) %\url{https://arxiv.org/abs/2107.07597}.
    \item Fai, T.G., \textbf{Park, Y.} ``Global asymptotic stability of an active disassembly model of flagellar length control.'' Journal of Mathematical Biology 84.8 (2021). %\url{https://arxiv.org/abs/2010.08163}.
    \item \textbf{Park, Y.}, Wilson, D. ``High-Order Accuracy Computation of Coupling Functions for Strongly Coupled Oscillators.'' SIADS 20.3:1464-1484 (2021).
    \item \textbf{Park, Y.}, Fai, T.G. ``The Dynamics of Vesicles Driven Into Closed Constrictions by Molecular Motors.'' Bulletin of Mathematical Biology. 82.141 (2020).
    \item \textbf{Park, Y.}, Geffen, M.N. ``A Circuit Model of Auditory Cortex.'' PLOS Computational Biology. 17.6:e1008016 (2020).
    \item Ermentrout, G.B.,  \textbf{Park, Y.}, Wilson, D. ``Recent advances in coupled oscillator theory.'' Philosophical Transactions A. 377. (2019).
    \item \textbf{Park, Y.}, Ermentrout, G.B. ``A Multiple Timescales Approach to Bridging Spiking- and Population-level Dynamics.'' Chaos. 28.8:083123 (2018).
    \item \textbf{Park, Y.}, Ermentrout, G.B. ``Scalar Reduction of a Neural Field Model with Spike Frequency Adaptation.'' SIADS 17.1:931--981 (2018).
    \item \textbf{Park, Y.}, Shaw, K.M. Chiel, H.J. Thomas, P.J. ``The Infinitesimal Phase Response Curve of Oscillators in Piecewise Smooth Dynamical Systems.'' EJAM 19.5:905--940 (2018).
    \item \textbf{Park, Y.}, Ermentrout, G.B. ``Weakly Coupled Oscillators in a Slowly Varying World.'' Springer Journal of Computational Neuroscience 40.3:269--281 (2016).
    \item Shaw, K.M., \textbf{Park, Y-M.}, Chiel, H.J., Thomas, P.J. ``Phase Resetting in an Asymptotically Phaseless System: On the Phase Response of Limit Cycles Verging on a Heteroclinic Orbit." SIADS 11.1:350--91 (2012).
\end{enumerate}

\textbf{Submitted}
\begin{enumerate}[leftmargin=.225in,rightmargin=.1in,itemsep=2pt]   
\item Models of Vimentin Organization Under Actin-Driven Transport. Park, Y., Leduc, C., Etienne-Manneville, S., and Portet, S.
\end{enumerate}

%\textbf{Under Review:}
%\begin{enumerate}[leftmargin=.225in,rightmargin=.1in,itemsep=2pt]   
%\end{enumerate}
%\newpage

\section{Book Chapters}
\noindent
\renewcommand\labelitemi{\tiny$\bullet$}
\begin{enumerate}[leftmargin=.225in,rightmargin=.1in,itemsep=2pt]
    \item \textbf{Park, Y.}, Heitmann, S., Ermentrout, G.B. ``The Utility of Phase Models in Studying Neural Synchronization.'' Book chapter in ``Computational Models of Brain and Behavior''. Wiley-Blackwell 493--505 (2017).
\end{enumerate}


\section{Teaching}
\begin{tabular}{p{0.18\linewidth}p{0.08\linewidth}p{0.4\linewidth}p{.2\linewidth}}
\textbf{School} & \textbf{Type} & \textbf{Class} & \textbf{Term(s)}\\
\noalign{\global\arrayrulewidth=.1mm}
\arrayrulecolor{gray}\hline
U. Florida & Lecture & Linear Algebra & Fall 2022 \\
\arrayrulecolor{gray}\hline
U. Manitoba & Lecture & Ordinary Differential Equations & Fall 2021 \\
 & Lecture & Partial Differential Equations & Fall 2021 \\
 \arrayrulecolor{gray}\hline
Marine Biol. Lab. & Assistant & Methods in Comp. Neuroscience & Summer 2021 \\
  \arrayrulecolor{gray}\hline
Brandeis &   {Lecture} & Calculus 3 & Spring 2021 \\
  & {Lecture} & Linear Algebra & Spring 2020 \\
\noalign{\global\arrayrulewidth=.1mm}
  \arrayrulecolor{gray}\hline
U. Pitt.  & {Lecture} & Differential Equations (3 sections) & Summers, 2014--2017\\
& & Linear Algebra & Summer 2015 \\
& & Discrete Math & Spring 2015 \\
& Recitation & Computational Neuroscience & Summers, 2014--2017 \\
&  & Business Calculus (6 sections) & Fall/Spring 2013/16\\
&  & Calculus 1, 2, 3 (6 sections) & Fall/Spring 2014--2016\\
& Grading & Differential Equations (10 sections) & Fall/Spring 2013--2017  \\
& & Complex Variables and Applications & Spring 2017 \\
& & Linear Algebra (2 sections) & Spring 2016\\
\noalign{\global\arrayrulewidth=.1mm}
  \arrayrulecolor{gray}\hline
Oberlin & Assistant & Computational Neuroscience  & Winter 2013\\
\noalign{\global\arrayrulewidth=.1mm}
  \arrayrulecolor{gray}\hline
Case Western & Assistant & Calculus 3  & Spring 2012 
\end{tabular}

\section{Honors and Awards}
\begin{tabular}{p{0.18\linewidth}p{0.75\linewidth}}
\textsc{2021} & Society for Mathematical Biology poster prize\\
\textsc{Sep. 2021--Aug. 2023} & PIMS Postdoctoral Fellowship\\
\textsc{2021} & SIAM Early Career Travel Award\\
\textsc{Sep. 2017--May 2018} & Andrew Mellon Predoctoral Fellowship\\
\textsc{2017} & SIAM Student Travel Award\\
\textsc{2016} & Elizabeth Baranger Teaching Award (nominated)\\
\textsc{2012} & SPUR (Summer Program for Undergraduate Research)\\
%\textsc{2010--2012} & Choose Ohio First Scholarship\\
%\textsc{2009--2012} & Dean's High Honors
\end{tabular}

\section{Oral Presentations}
\begin{itemize}[leftmargin=.225in,rightmargin=.1in]
    \item ``Models of Vimentin Organization Under Actin-Driven Transport''
    \begin{itemize}
        \item {\makebox[2cm]{September 2022\hfill} U. Florida Biomathematics Seminar, Gainesville, FL}
        \item {\makebox[2cm]{May 2022\hfill} Canadian Mathematical Society Summer Meeting, St. Johns, Newfoundland}
    \end{itemize}
    \item ``High-Order Accuracy Computation of Coupling Functions for Strongly Coupled Oscillators''
    \begin{itemize}
        \item {\makebox[2cm]{May 2021\hfill} SIAM Dynamical Systems (virtual)}
    \end{itemize}
    \item ``Coarse-grained Stochastic Model of Myosin-Driven Vesicles into Dendritic Spines''
    \begin{itemize}
        \item {\makebox[2cm]{Mar. 2021\hfill} SIAM CSE (virtual)}
    \end{itemize}
    \item ``Scalar Reduction of a Neural Field Model with Spike Frequency Adaptation''
    \begin{itemize}
        \item {\makebox[2cm]{Mar. 2020\hfill} Boston University Dynamics Seminar (Cancelled due to COVID-19)}
        \item {\makebox[2cm]{Jul. 2019\hfill} Society for Mathematical Biology, University of Montreal}
        \item {\makebox[2cm]{May 2019\hfill} SIAM Dynamical Systems, Snowbird, Utah}
        \item {\makebox[2cm]{Mar. 2016/17\hfill} U. Pitt. Mathematical Biology Seminar}
    \end{itemize}
    \item ``A Multiple Timescales Approach to Bridging Spiking- and Population-level Dynamics''
    \begin{itemize}
        \item {\makebox[2cm]{Mar. 2018\hfill} U. Pitt. Mathematical Biology Seminar}
    \end{itemize}
    \item ``The Dynamics of Vesicles Driven through Closed Constrictions by Molecular Motors''
    \begin{itemize}
        \item {\makebox[2cm]{Aug. 2020\hfill} Society for Mathematical Biology (virtual)}
        \item {\makebox[2cm]{Jun. 2020\hfill} SIAM Life Sciences (virtual)}
        \item {\makebox[2cm]{Jun. 2020\hfill} Brandeis Mathematical Biology Seminar, Waltham, MA}
        \item {\makebox[2cm]{Jan. 2020\hfill} Aspen Center for Physics, Aspen, CO}
        \item {\makebox[2cm]{Nov. 2019\hfill} APS Fluids, Seattle, WA}
        \item {\makebox[2cm]{Aug. 2019\hfill} Society for Mathematical Biology (virtual)}
    \end{itemize}
    \item ``Weakly Coupled Oscillators in a Slowly Varying World''
    \begin{itemize}
         \item {\makebox[2cm]{Sep. 2018\hfill} Computational Neuroscience Initiative Seminar, Philadelphia, PA}
         \item {\makebox[2cm]{May 2015/17\hfill} SIAM Dynamical Systems, Snowbird, Utah}
         \item {\makebox[2cm]{Mar. 2015\hfill} U. Pitt. Mathematical Biology Seminar}
    \end{itemize}
    \item  ``The Infinitesimal Phase Response Curve of Oscillators in Piecewise Smooth Dynamical Systems''
    \begin{itemize}
        \item {\makebox[2cm]{Jul. 2017\hfill} SIAM Annual Meeting, Pittsburgh, PA}
    \end{itemize}
\end{itemize}






\section{Service}
\begin{tabular}{p{0.18\linewidth}p{0.8\linewidth}}
\textsc{Jul. 2021} & Judge for poster presentations at SMB 2021\\
\textsc{Jun. 2019--Jul. 2020} & Organizer of the Brandeis Math Bio Seminar\\
\textsc{Jul. 2019--Pres.} & Volunteer advisory member of the SMB Neuroscience Subgroup\\
\textsc{Jul. 2019} & Judge for poster presentations at SMB 2019 Montreal\\
\textsc{Apr. 2019} & Guest lecturer, Science Outreach, Moder Patshala \& Free Library of Philadelphia.\\
\textsc{Jul. 2017} & Volunteer kit-stuffing at the SIAM Annual Meeting\\
\textsc{Mar. 2017} & Volunteer lifeline at the Pitt Integration Bee
%\textsc{2010--2012} & Choose Ohio First Scholarship\\
%\textsc{2009--2012} & Dean's High Honors
\end{tabular}

\section{Conferences and Posters}
\begin{longtable}{p{0.18\linewidth}p{0.8\linewidth}}
\textsc{Jun.} 2021 & Poster, Society for Mathematical Biology, University of Montreal\\
\textsc{Jun.} 2019 & Attendance, 79th New England Complex Fluids, Boston University\\
\textsc{Nov.} 2019 & Attendance, CMSA Workshop, Harvard University\\
\textsc{Mar.} 2019 & Poster, MINS Symposium Philadelphia, Pennsylvania\\
\textsc{Sep.} 2018 & Poster, Auditory SPLASH Conference Philadelphia, Pennsylvania\\
\textsc{May.} 2015 & Poster, SIAM: Dynamical Systems Snowbird, Utah\\
\textsc{May.} 2011 & Attendance, SIAM: Dynamical Systems, Snowbird, Utah\\
\textsc{Aug.} 2010 & Oral presentation, Mathematical Association of America MathFest, Pittsburgh, PA\\
\textsc{Jul.} 2010 & Attendance, SIAM: Life Sciences, Pittsburgh, PA
\end{longtable}


\updateinfo
\vspace{-.2in}
\end{document}
